The Concurrent Calculi Formalisation Benchmark

### 2024-02-03 short-paper/short-paper.tex
added references for infinitary proof systems/logics

\paragraph{Addressing new calculi and new features.}
\todo{Maybe cite some references in this section? Mention the higher-order pi calculus?}
Extending in this direction means proposing new challenges covering different features of process calculi, or different proof mechanisation features.
Some interesting aspects of message-passing calculi to be explored in further challenges could be multiparty session types and choreographies, as their meta-theory includes aspects -- \eg, well-formedness conditions on global types, partiality of end-point projection function, etc. -- that we do not address here.
Also, one could easily design a challenge that goes beyond our coinduction challenge, by exploring different notions of bisimilarity (barbed, weak, \etc) and trace equivalence.
%
\luca{Coinduction may also play a relevant role in supporting recursive
processes and session types. Indeed, it is often the case that session type
systems (and logics) with recursive session types (and propositions) are
naturally expressed in \emph{infinitary form} by interpreting their typing (and
proof) rules coinductively. I CAN ADD ONE OR TWO REFERENCES IF YOU FEEL IT'S APPROPRIATE}

>>>>

\paragraph{Addressing new calculi and new features.}
\todo{Maybe cite some references in this section? Mention the higher-order pi calculus?}
Extending in this direction means proposing new challenges covering different features of process calculi, or different proof mechanisation features.
Some interesting aspects of message-passing calculi to be explored in further challenges could be multiparty session types and choreographies, as their meta-theory includes aspects -- \eg, well-formedness conditions on global types, partiality of end-point projection function, etc. -- that we do not address here.
Also, one could easily design a challenge that goes beyond our coinduction challenge, by exploring different notions of bisimilarity (barbed, weak, \etc) and trace equivalence.
%
Coinduction may also play a relevant role in supporting recursive processes and
session types. Indeed, it is often the case that session type systems (and
logics) with recursive session types (and propositions) are naturally expressed
in \emph{infinitary form} by interpreting their typing (and proof) rules
coinductively~\cite{BaeldeDoumaneSaurin16,DerakhshanPfenning22,HornePadovani23}.
